Visualizing probability distributions across bivariate nonlinear temporal granularities

### 2020-02-24 main.Rmd
minor changes in Section 2 for content cut

```{r linear-time, echo=FALSE, out.width = "100%", fig.cap="The time domain distributed as linear granularities."}
knitr::include_graphics("Figs/linear-arr.png")
```

@@

A discrete time model often uses a fixed smallest granularity also known as _*bottom granularity_* (@Bettini1998-ed) so that the the underlying time domain can be described as a sequence of non-decomposable, consecutive time intervals of some fixed, minimal duration called _*chronons*_ (@Jensen1998-qn). Chronons may be grouped into granules and a linear granularity is a non-overlapping mapping of 
granules to subsets of the time domain (see @Dyreson2000-mr). A system of multiple granularities in lattice structures is referred to as a calendar.

@@

Linear time granularities are computed through an algebraic representation for time granularities, which is referred to as calendar algebra [@Ning2002-tf]. It is assumed that there exists a “bottom” granularity and calendar algebra operations are designed to generate new granularities recursively from the bottom up.

@@

In addition to the integer index, each granule could be associated with a textual representation which is called the label. The label can be mapped to index for input and the index can later be mapped to this label for output. When the label set is exactly the integers, the granularities are called "full-integer" labeled granularity, such as in Definition \ref{def:linear}. Some calendar operations will only work on full-integer labeled granularities, while others can be implemented using more flexible labelings.

<!-- CONTENT CUT -->
<!-- The notion of a labeled granularity is introduced in @Bettini2000-qk to simplify the calendar algebra. A labeled granularity is a pair $(L, G)$, where the label set $L$ is a subset of the integers instead of the set of integers and -->
<!-- follows the conditions (1) and (2) in \ref{def:linear} where $i$, $j$, and $k$ are in $L$. When the label set $L$ is exactly the integers, the granularities are called "full-integer" labeled granularity, such as in Definition \ref{def:linear}.<!-- However, the set $L$ of labels can be an arbitrary subset of (possibly non contiguous) integers and could be used to identify granules.-->  -->

@@

Some relevant calendar algebra operations are discussed below; these will be used in Section \ref{sec:cyclic-gran} to define circular and aperiodic granularities.

@@

For more variations of grouping operations and granule oriented operations, see @Ning2002-tf.

>>>>

```{r linear-time, echo=FALSE, out.width = "100%", fig.cap="The time domain distributed as linear granularities."}
knitr::include_graphics("Figs/linear-arr.png")
```
In addition to the integer index, each granule could be associated with a textual representation which is called the label. The label can be mapped to index for input and the index can later be mapped to this label for output. When the label set is exactly the integers, the granularities are called "full-integer" labeled granularity, such as in Definition \ref{def:linear}.<!-- Some calendar operations will only work on full-integer labeled granularities, while others can be implemented using more flexible labelings.-->

@@

A discrete time model often uses a fixed smallest granularity also known as *_bottom granularity_* (@Bettini1998-ed) so that the the underlying time domain can be described as a sequence of non-decomposable, consecutive time intervals of some fixed, minimal duration called *_chronons_* (@Jensen1998-qn). Chronons may be grouped into granules and a non-overlapping mapping of granules to subsets of the time domain is a linear granularity. A system of multiple granularities in lattice structures is referred to as a *_calendar_* (see @Dyreson2000-mr).

@@

Linear time granularities are computed through an algebraic representation for time granularities, which is referred to as calendar algebra [@Ning2002-tf]. It is assumed that there exists a *_bottom granularity_* and calendar algebra operations are designed to generate new granularities recursively from the bottom up. Some relevant calendar algebra operations are discussed below; these will be used in Section \ref{sec:cyclic-gran} for illustrations in circular and aperiodic granularities.

@@

<!-- CONTENT CUT -->
<!-- The notion of a labeled granularity is introduced in @Bettini2000-qk to simplify the calendar algebra. A labeled granularity is a pair $(L, G)$, where the label set $L$ is a subset of the integers instead of the set of integers and -->
<!-- follows the conditions (1) and (2) in \ref{def:linear} where $i$, $j$, and $k$ are in $L$. When the label set $L$ is exactly the integers, the granularities are called "full-integer" labeled granularity, such as in Definition \ref{def:linear}.<!-- However, the set $L$ of labels can be an arbitrary subset of (possibly non contiguous) integers and could be used to identify granules.-->

@@

@@

For more variations of calendar algrabra operations, see @Ning2002-tf.
